A Logistic Regression Approach to CoIL Challenge 2000

### 2019-12-03 final project/Draft.Rmd
Corrected typo

  MOSTYPE_labels <- c("1" = "1 High Income, expensive child",
                      "2" = "2 Very Important Provincials",
                      "3" = "3 High status seniors",
                      "4" = "4 Affluent senior apartments",
                      "5" = "5 Mixed seniors",
                      "6" = "6 Career and childcare",
                      "7" = "7 Dinki's (double income no kids)",
                      "8" = "8 Middle class families",
                      "9" = "9 Modern, complete families",
                      "10" = "10 Stable family",
                      "11" = "11 Family starters",
                      "12" = "12 Affluent young families",
                      "13" = "13 Young all american family",
                      "14" = "14 Junior cosmopolitan",
                      "15" = "15 Senior cosmopolitans",
                      "16" = "16 Students in apartments",
                      "17" = "17 Fresh masters in the city",
                      "18" = "18 Single youth",
                      "19" = "19 Suburban youth",
                      "20" = "20 Etnically diverse",
                      "21" = "21 Young urban have-nots",
                      "22" = "22 Mixed apartment dwellers",
                      "23" = "23 Young and rising",
                      "24" = "24 Young, low educated", 
                      "25" = "25 Young seniors in the city",
                      "26" = "26 Own home elderly",
                      "27" = "27 Seniors in apartments",
                      "28" = "28 Residential elderly",
                      "29" = "29 Porchless seniors: no front yard",
                      "30" = "30 Religious elderly singles",
                      "31" = "31 Low income catholics",
                      "32" = "32 Mixed seniors",
                      "33" = "33 Lower class large families",
                      "34" = "34 Large family, employed child",
                      "35" = "35 Village families",
                      "36" = "36 Couples with teens 'Married with children'",
                      "37" = "37 Mixed small town dwellers",
                      "38" = "38 Traditional families",
                      "39" = "39 Large religous families",
                      "40" = "40 Large family farms",
                      "41" = "41 Mixed rurals")

>>>>

  MOSTYPE_labels <- c("1" = "1 High Income, expensive child",
                      "2" = "2 Very Important Provincials",
                      "3" = "3 High status seniors",
                      "4" = "4 Affluent senior apartments",
                      "5" = "5 Mixed seniors",
                      "6" = "6 Career and childcare",
                      "7" = "7 Dinki's (double income no kids)",
                      "8" = "8 Middle class families",
                      "9" = "9 Modern, complete families",
                      "10" = "10 Stable family",
                      "11" = "11 Family starters",
                      "12" = "12 Affluent young families",
                      "13" = "13 Young all american family",
                      "14" = "14 Junior cosmopolitan",
                      "15" = "15 Senior cosmopolitans",
                      "16" = "16 Students in apartments",
                      "17" = "17 Fresh masters in the city",
                      "18" = "18 Single youth",
                      "19" = "19 Suburban youth",
                      "20" = "20 Ethnically diverse",
                      "21" = "21 Young urban have-nots",
                      "22" = "22 Mixed apartment dwellers",
                      "23" = "23 Young and rising",
                      "24" = "24 Young, low educated", 
                      "25" = "25 Young seniors in the city",
                      "26" = "26 Own home elderly",
                      "27" = "27 Seniors in apartments",
                      "28" = "28 Residential elderly",
                      "29" = "29 Porchless seniors: no front yard",
                      "30" = "30 Religious elderly singles",
                      "31" = "31 Low income catholics",
                      "32" = "32 Mixed seniors",
                      "33" = "33 Lower class large families",
                      "34" = "34 Large family, employed child",
                      "35" = "35 Village families",
                      "36" = "36 Couples with teens 'Married with children'",
                      "37" = "37 Mixed small town dwellers",
                      "38" = "38 Traditional families",
                      "39" = "39 Large religous families",
                      "40" = "40 Large family farms",
                      "41" = "41 Mixed rurals")
